
\documentclass[letterpaper]{article}

\setlength{\oddsidemargin}{-0.35in}
\setlength{\textwidth}{7in}
\setlength{\textheight}{11in}
\setlength{\topmargin}{-0.7in}
\setlength{\headheight}{0in}


\begin{document}

\vspace{0.25in}

\begin{flushleft}
Nicholas Maxwell \hfill Departments of Mathematics and Physics \\
Curriculum Vitae \hfill  University of Houston, Houston, Texas \\
\hrulefill
\end{flushleft}

\begin{flushleft}
Citizenship : U.S.A., U.K.\\
Phone : (281)-795-1172\\
E-mail : \\
\hspace{0.25in} nicholas.maxwell@gmail.com\\
\hspace{0.25in} nmaxwell@math.uh.edu\\
Mailing address : \\
\hspace{0.25in} 9502 Steep Bank Passage,\\
\hspace{0.25in} Missouri City, TX, 77459
\end{flushleft}

\section*{Education}

\begin{flushleft}
\hspace{0.25in} {\bf B.S. Physics}, 2009, U. of H.\\
\end{flushleft}
\begin{flushleft}
\hspace{0.25in} {\bf B.S. Mathematics}, 2009, U. of H. (GPA: 3.4, last 60 hours )
\end{flushleft}
\begin{flushleft}
\hspace{0.25in} {\bf Graduate School in Mathematics}, 2009 - present, U. of H  (GPA: 3.56     ).
\end{flushleft}

\section*{Research}

\begin{flushleft}
\hspace{0.25in} {\bf Graduate student (RA)}, fall 2009 - present, under Dr. B. G. Bodmann \& Dr. Donald Kouri \\
\vspace{0.15in} 
\hspace{0.75in} Solutions of the Helmholz equation via functional integration techniques.\\
\vspace{0.15in} 
\hspace{0.75in} Solutions of the general elastic wave equation by polynomial approximation of the solution operator. \\
\vspace{0.15in} 
\hspace{0.75in} During the summer of 2010 I attended an internship under the direction of Dr. Laurent Demanet, \\
\hspace{0.75in} we applied new fast algorithms, developed in part by Dr. Demanet, for evaluating general oscilliatory \\
\hspace{0.75in} integral operators to synthetic aperture radar data, for applications in radar imaging. \\
%\hspace{0.75in}
\vspace{0.15in} 
\hspace{0.25in} {\bf Undergraduate research assistant}, fall 2008 - summer 2009, with Dr. Donald Kouri\\
\vspace{0.15in} 
\hspace{0.75in} Quantum mechanical eigenvalue problems applied to several original research projects.\\
\vspace{0.15in}
\hspace{0.75in} Propagator-based approaches to solving the acoustic wave equation, for specific application in the\\
\hspace{0.75in} seismic industry.\\
%\vspace{0.15in}
%\hspace{0.25in} {\bf Main interests}\\
%\vspace{0.15in}
%\hspace{0.75in} Computation, signal analysis, computer science.\\
%\vspace{0.15in}
%\hspace{0.25in} {\bf General interests}\\
%\vspace{0.15in}
%\hspace{0.75in} Electrodynamics, mathematical and statistical physics, quantum theory.\\
%\hspace{0.75in} Functional analysis, linear algebra, P.D.Es, electrical engineering, programming.
\end{flushleft}


\section*{Work History}

\begin{flushleft}
\hspace{0.25in} {\bf MIT, AFRL (Wright-Patterson Air Force Base)}, Summer 2010\\
\end{flushleft}
%\begin{flushleft}
%\hspace{0.25in} {\bf Erdos Miller}, July 2009 - present\\
%\vspace{0.15in}
%\hspace{0.75in} Research consultant: Applied physics and signal analysis. \\
%\end{flushleft}
\begin{flushleft}
\hspace{0.25in} {\bf ION Geophysical}, May 2005 - sept. 2008\\
\vspace{0.15in}
\hspace{0.75in} Engineering intern. \\
\end{flushleft}
\begin{flushleft}
\hspace{0.25in} {\bf CGG Veritas}, 2006 - 2008\\
%\vspace{0.15in}
%\hspace{0.75in} Contracted engineering and drafting work.
\end{flushleft}
\begin{flushleft}
\hspace{0.25in} {\bf Precision Tube Technology}, 2004 - 2005 \\
%\vspace{0.15in}
%\hspace{0.75in} Q.C. tech.
\end{flushleft}

\section*{Publications}
\begin{flushleft}
\hspace{0.25in} D. J. Kouri, T. Markovich, N. Maxwell, B. G. Bodmann, {\it The Heisenberg-Weyl Algebra on the Circle and\\
\hspace{0.25in}  a Related Quantum Mechanical Model for Hindered Rotation}, \textit{J. Phys. Chem. A, 113, 7698-7705}, (2009).\\
\vspace{0.15in}
\hspace{0.25in} D. J. Kouri, T. Markovich, N. Maxwell, E. Bittner, {\it Supersymmetric Quantum Mechanics for a General \\
\hspace{0.25in}    Family of Anharmonic Oscillator Models}, \textit{J. Phys. Chem. A, 113, 15257-15264}, (2009)\\
\vspace{0.15in}
\hspace{0.25in} Laurent Demanet, Matthew Ferrara, Nicholas Maxwell, Jack Poulson, Lexing Ying, {\it A butterfly algorithm \\
\hspace{0.25in} for synthetic aperture radar imaging}, submitted (2010) \\
\end{flushleft}







\end{document}
