
\documentclass[11pt]{article}

\setlength{\oddsidemargin}{-0.3in}
\setlength{\textwidth}{7in}
\setlength{\textheight}{11in}
\setlength{\topmargin}{-0.7in}
\setlength{\headheight}{0in}


\begin{document}

\vspace{2in}

\begin{flushright}
{\bf Nicholas Maxwell} \hfill Departments of Mathematics and Physics \\
 Jan. 15, 2010 \hfill  University of Houston, Houston, Texas \\
 \hfill  9502 Steep Bank Passage,\\
 \hfill Missouri City, TX, 77459 \\
 \hfill  namaxwell@uh.edu\\
\end{flushright}


\begin{flushleft}
Laurent Demanet,\\
Assistant Professor of Applied Mathematics \\
Massachusetts Institute of Technology \\
77 Massachusetts Avenue, Building 2, Room 392\\
Cambridge, MA 02139
\end{flushleft}


\begin{flushleft}
Dr. Demanet,\\
\end{flushleft}


I am a graduate student at the University of Houston, in mathematics; I'd like to apply for the summer intern position posted on your website. My graduate advisors are Dr. Bernard Bodmann and Dr. Donald Kouri, I have a bachelor of science in mathematics and physics.

Dr. Bodmann and I are investigating the application of stochastic differential equations to the general acoustic wave equation, which so far has been mostly theoretical work. My research with Dr. Kouri, has been in applying propagator based methods to the general elastic wave equation, using wavelets, derived by minimizing their uncertainty product; Dr. Kouri's main background is in quantum reactive scattering. The work I've done with Dr. Kouri has been computationally demanding, and I feel I have developed a strong interest and ability in this area, specifically in applying theory in a computational and numerical setting.

In addition to graduate school and research, I've been working on several contract research project for Erdos Miller, a recently founded engineering and consultation firm. The main project I've worked on has been to design and implement filter and decoding algorithms to be used in mud pulse telemetry, in Measurement While Drilling systems.

I have a solid background in programming, mostly in C/C++, lately I've been very interested in Python. I have certainly used Matlab and Fortran, but have not jet had the need to use either intensively, these are not difficult to expand on. I have kept my recent work here, if you are interested: ``http://github.com/nmaxwell''.

I don't yet have a specific career plan, generally I see my self working in an industrial research and development setting; I enjoy having a diverse range of technical projects to work on. I am considering a career involved in the seismic imaging industry. 

 I should be available starting the regular academic summer, through early August, giving time for preliminary exams. Thank you for considering me as a candidate for your internship position.


\begin{flushleft}
Sincerely, \\
Nick Maxwell
\end{flushleft}





\end{document}  
