
\documentclass[11pt]{article}

\setlength{\oddsidemargin}{-0.3in}
\setlength{\textwidth}{7in}
\setlength{\textheight}{11in}
\setlength{\topmargin}{-0.7in}
\setlength{\headheight}{0in}


\begin{document}

\vspace{2in}

\begin{flushright}
{\bf Nicholas Maxwell} \hfill Departments of Mathematics and Physics \\
 Jan. 15, 2011 \hfill  University of Houston, Houston, Texas \\
 \hfill  9502 Steep Bank Passage,\\
 \hfill Missouri City, TX, 77459 \\
 \hfill  nmaxwell@math.uh.edu\\
\end{flushright}


%\begin{flushleft}
%Laurent Demanet,\\
%Assistant Professor of Applied Mathematics \\
%Massachusetts Institute of Technology \\
%77 Massachusetts Avenue, Building 2, Room 392\\
%Cambridge, MA 02139
%\end{flushleft}


\begin{flushleft}
Dear Sir or Madam,\\
\end{flushleft}


I am writing to apply to the Gene Golub Summer School 2011. I am a graduate student at the University of Houston, in mathematics. My graduate advisors are Dr. Bernard Bodmann and Dr. Donald Kouri, I hold bachelor of science degrees in mathematics and in physics, and am working towards a Ph.D in mathematics.

My research has focused on the forward solutions of wave equations, with application in seismic imaging; our research group is funded by Petroleum Geo-Services, and Total. During the summer of 2010 I attended an internship under the direction of Dr. Laurent Demanet and Matthew Ferrara. I spent one month at MIT and two months at the Air Force Research Lab at the Wright-Patterson Air Force Base. The work was to apply a fast butterfly algorithm, developed to evaluate Fourier integral operators, to image synthetic aperture radar data using backprojection. During the internship Dr. Demanet suggested I apply to the Gene Golub Summer School this year. I would be very excited to attend the summer school, as it is clearly relevant to the work I'm doing, and my interests generally.

If I am accepted, it is not clear if monies will be available from my advisor to cover travel or housing expenses. However, if the need arises, I may personally be able to cover the expenses, but early notification would be helpfull.

Thank you for your consideration.

\begin{flushleft}
Sincerely, \\
Nick Maxwell
\end{flushleft}





\end{document}  
